Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-09 appendix/appendix.tex
Bib restructure
Appendix fix

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment                 & Version                       \\ [0.5ex]
        \hline\hline
        $\lambda_N$                 & 2.1989                        \\
        $\kappa_{N\beta}$           & 3.9627                        \\
        $\mu_N$                     & 1.7219                        \\
        $\nu_{N\Phi}$  0.2195       & $cell^{-1}\cdotp h^{-1}$      \\
        \hline
        $\lambda_\Phi$              & 1.3146  $cell/h$              \\
        $\kappa_{\Phi\beta}$ 0.1235 & $cell/(unit\cdotp h)$         \\
        $\mu_\Phi$  0.1454          & $h^{-1}$                      \\
        \hline
        $s_{\beta N}$               & 6.5536  $unit/(cell\cdotp h)$ \\
        $i_{\beta\Phi}$  1.7062     & $cell^{-1}$                   \\
        $\mu_\beta$                 & 0.5212  $h^{-1}$              \\
        \hline
        $s_{\alpha\Phi}$  10.2416   & $unit/(cell\cdotp h)$         \\
        $\mu_\alpha$ 19.6642        & $h^{-1}$                      \\
        [1ex]
        \hline
    \end{tabular}
    \caption{Environment on local machine}
    \label{table:local_macine}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment                 & Version                       \\ [0.5ex]
        \hline\hline
        $\lambda_N$                 & 2.1989                        \\
        $\kappa_{N\beta}$           & 3.9627                        \\
        $\mu_N$                     & 1.7219                        \\
        $\nu_{N\Phi}$  0.2195       & $cell^{-1}\cdotp h^{-1}$      \\
        \hline
        $\lambda_\Phi$              & 1.3146  $cell/h$              \\
        $\kappa_{\Phi\beta}$ 0.1235 & $cell/(unit\cdotp h)$         \\
        $\mu_\Phi$  0.1454          & $h^{-1}$                      \\
        \hline
        $s_{\beta N}$               & 6.5536  $unit/(cell\cdotp h)$ \\
        $i_{\beta\Phi}$  1.7062     & $cell^{-1}$                   \\
        $\mu_\beta$                 & 0.5212  $h^{-1}$              \\
        \hline
        $s_{\alpha\Phi}$  10.2416   & $unit/(cell\cdotp h)$         \\
        $\mu_\alpha$ 19.6642        & $h^{-1}$                      \\
        [1ex]
        \hline
    \end{tabular}
    \caption{Environment on remote machine}
    \label{table:remote_macine}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Value & Unit                     \\ [0.5ex]
        \hline\hline
        $\lambda_N$          & 2.20  & $cell/h$                 \\
        $\kappa_{N\beta}$    & 3.96  & $cell/(unit\cdotp h)$    \\
        $\mu_N$              & 1.72  & $h^{-1}$                 \\
        $\nu_{N\Phi}$        & 0.220 & $cell^{-1}\cdotp h^{-1}$ \\
        \hline
        $\lambda_\Phi$       & 1.31  & $cell/h$                 \\
        $\kappa_{\Phi\beta}$ & 0.124 & $cell/(unit\cdotp h)$    \\
        $\mu_\Phi$           & 0.145 & $h^{-1}$                 \\
        \hline
        $s_{\beta N}$        & 6.554 & $unit/(cell\cdotp h)$    \\
        $i_{\beta\Phi}$      & 1.71  & $cell^{-1}$              \\
        $\mu_\beta$          & 0.521 & $h^{-1}$                 \\
        \hline
        $s_{\alpha\Phi}$     & 10.2  & $unit/(cell\cdotp h)$    \\
        $\mu_\alpha$         & 19.1  & $h^{-1}$                 \\
        \hline
    \end{tabular}
    \caption{Parameter values used for model 1}
    \label{table:m1}
\end{table}

@@

\begin{figure}[h!]

>>>>

\begin{table}[H]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment        & Version                \\ [0.5ex]
        \hline\hline
        Operating system   & macOS Catalina 10.15.6 \\
        PyCharm (IDE)      & Professional 202.2     \\
        Python interpretor & 3.7.0                  \\
        IPython            & 7.12.0                 \\
        Clang              & 6.0 (clang-600.0.57)   \\
        \hline
    \end{tabular}
    \caption{Environment on local machine}
    \label{table:local_macine}
\end{table}

Version requirements for some critical site packages (\verb|Python|) used in the code are listed in Table \ref{table:local_package}.

\begin{table}
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment & Version         \\ [0.5ex]
        \hline\hline
        pyABC       & $\simeq$ 0.10.3 \\
        NumPy       & $\simeq$ 1.18.4 \\
        SciPy       & $\simeq$ 1.4.1  \\
        pandas      & $\simeq$ 1.1.0  \\
        matplotlib  & $\simeq$ 3.0.1  \\
        bokeh       & $=$ 1.4.0       \\
        \hline
    \end{tabular}
    \caption{Site packages on local machine}
    \label{table:local_package}
\end{table}

Local development and some runs of small size were done under the hardware listed in Table \ref{table:local_hardware}. When running ABC SMC, the program can make used of 8 python process (Hyper-Threading enabled) and run under 3.8GHz (maximal) for a long time under proper cooling, proved that the program could efficiently use the computation resources for a local personal computer. It is noted that the program took no advantage of graphics card, as \verb|multiprocessing| along can out exploit the resources inside CPU. The execution time and other performance data presented in Chapter 5 were obtained using remote machines but not local machine.

\begin{table}
    \centering
    \begin{tabular}{|c c|}
        \hline
        Hardware        & Detail                                \\ [0.5ex]
        \hline\hline
        CPU             & Quad-Core Intel Core i5 8259U 2.3 GHz \\
        Architecture    & 64 Bit                                \\
        Hyper-Threading & Supported                             \\
        Turbo Boost     & Max 3.8 GHz                           \\
        Memory          & 16 GB                                  \\
        Graphics card   & Iris Plus Graphics 655                \\
        \hline
    \end{tabular}
    \caption{Hardwares on local machine}
    \label{table:local_hardware}
\end{table}

@@

\begin{table}[H]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment                 & Version                       \\ [0.5ex]
        \hline\hline
        Placeholder                 & 2\\
        \hline
    \end{tabular}
    \caption{Environment on remote machine}
    \label{table:remote_macine}
\end{table}

@@

\begin{table}[H]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Value & Unit                     \\ [0.5ex]
        \hline\hline
        $\lambda_N$          & 2.20  & $cell/h$                 \\
        $\kappa_{N\beta}$    & 3.96  & $cell/(unit\cdotp h)$    \\
        $\mu_N$              & 1.72  & $h^{-1}$                 \\
        $\nu_{N\Phi}$        & 0.220 & $cell^{-1}\cdotp h^{-1}$ \\
        \hline
        $\lambda_\Phi$       & 1.31  & $cell/h$                 \\
        $\kappa_{\Phi\beta}$ & 0.124 & $cell/(unit\cdotp h)$    \\
        $\mu_\Phi$           & 0.145 & $h^{-1}$                 \\
        \hline
        $s_{\beta N}$        & 6.554 & $unit/(cell\cdotp h)$    \\
        $i_{\beta\Phi}$      & 1.71  & $cell^{-1}$              \\
        $\mu_\beta$          & 0.521 & $h^{-1}$                 \\
        \hline
        $s_{\alpha\Phi}$     & 10.2  & $unit/(cell\cdotp h)$    \\
        $\mu_\alpha$         & 19.1  & $h^{-1}$                 \\
        \hline
    \end{tabular}
    \caption{Parameter values used for model 1}
    \label{table:synthetic_data}
\end{table}

@@

### 2020-08-09 background/background.tex
Appendix fix

 Preliminarily \verb|pyABC| \cite{ref:pyabc} in \verb|Python| was chosen for our first implementations.

>>>>

 Preliminarily \verb|pyABC| \cite{ref:pyabc} in \verb|Python| was chosen for implementations. \verb|pyABC| supports multiple types of parallelisation, e.g., multicore processing and distributed cluster, and supports resume stored runs, which made our experiments easier. It is well documented and flexible in customisations of the algorithm.

 Some other ABC SMC related packages were also examined and considered as backups, include ELFI \footnote{\url{https://elfi.readthedocs.io/en/latest/}}, ABC-SysBio \cite{ref:abcsysbio}, EasyABC\footnote{\url{https://cran.r-project.org/web/packages/EasyABC/index.html}}, GpABC \footnote{\url{https://github.com/tanhevg/GpABC.jl}}, etc. These packages may have their advantages (e.g. ABC-SysBio supports CUDA acceleration) and considered as alternative implementation methods, or can be used to compare performance difference.

 Additionally, some other softwares were also need for solving ODE, results analysis and visualisations. Some software and hardware environments are listed in Appendix A.
